### 2016-03-22 section/5_exper.tex
merge tables

\input section/tab_cover

@@

\subsection{Coverage Results}
\label{sec:coverage}
Overall, \Tool provides good diagnosis coverage, as shown in Table~\ref{tab:cover}. 
\Tool identifies the correct root cause for \textbf{all} \allbugs benchmarks, and 
suggests fix strategies that exactly match what developers took in practice
for 33 out of \allbugs cases.

@@

\input section/tab_top5

As shown in Table \ref{tab:top5}, \Tool is accurate, having 0 real
false positive and 22 benign false positives for all the top 5 loops
of the \allbugs benchmarks.

@@

Automated tools have been developed to detect inefficient loop bugs
\cite{Alabama, CARAMEL, IsilDillig.PLDI15}. 
As discussed in Section \ref{sec:intro}, although these tools are very
useful, they are not suitable for failure diagnosis. 
For example, Toddler~\cite{Alabama} only targets inefficient nested loops, and
hence can only cover about half of the bugs in our \emph{general} benchmark suite.
Being a dynamic tool, it also incurs 10X or more slowdowns, which is much more
expensive than \Tool. 
Caramel~\cite{CARAMEL} statically detects inefficient loops that can be fixed
by adding conditional-breaks. Very few bugs in Table \ref{tab:} are like this.
CLARITY~\cite{IsilDillig.PLDI15} statically detects redundant traversal bugs. 
We expect it to automatically detect a sub-set of the cross-loop redundancy
loops in our benchmark set, but not for other types of inefficient
loops. In summary, \Tool aims to explain performance problems that have 
already manifested,
yet bug detection tools aim to predict problems that may not have manifested.
\Tool achieves higher generality and accuracy at the cost of the prediction
capability.

>>>>

%\input section/tab_cover

@@

\subsection{Coverage Results}
\label{sec:coverage}
Overall, \Tool provides good diagnosis coverage, as shown in Table~\ref{tab:benchmarks}. 
\Tool identifies the correct root cause for \textbf{all} \allbugs benchmarks, and 
suggests fix strategies that exactly match what developers took in practice
for 33 out of \allbugs cases.

@@

%\input section/tab_top5

As shown in Table \ref{tab:benchmarks}, \Tool is accurate, having 0 real
false positive and 22 benign false positives for all the top 5 loops
of the \allbugs benchmarks.

@@

Automated tools have been developed to detect inefficient loop bugs
\cite{Alabama, CARAMEL, IsilDillig.PLDI15}. 
As discussed in Section \ref{sec:intro}, although these tools are very
useful, they are not suitable for failure diagnosis. 
For example, Toddler~\cite{Alabama} only targets inefficient nested loops, and
hence can only cover about half of the bugs in our \emph{general} benchmark suite.
Being a dynamic tool, it also incurs 10X or more slowdowns, which is much more
expensive than \Tool. 
Caramel~\cite{CARAMEL} statically detects inefficient loops that can be fixed
by adding conditional-breaks. Very few bugs in Table \ref{tab:root} are like this.
CLARITY~\cite{IsilDillig.PLDI15} statically detects redundant traversal bugs. 
We expect it to automatically detect a sub-set of the cross-loop redundancy
loops in our benchmark set, but not for other types of inefficient
loops. In summary, \Tool aims to explain performance problems that have 
already manifested,
yet bug detection tools aim to predict problems that may not have manifested.
\Tool achieves higher generality and accuracy at the cost of the prediction
capability.
